Stack Safety as a Security Property

### 2020-07-08 main.tex
A pass on sections 1-4
Small comments and nits, harmonized notation and spelling.

But what {\em is} this ``stack safety'' of which we speak? Precise formal
definitions are lacking in the literature; instead, the notion
is usually defined negatively, by enumerating the bad things that a given
enforcement mechanism
prevents, such as corruption of return addresses, buffer overflows, or
use of uninitialized variables.
%with the notion usually being
%defined negatively: through examples of stack-based exploits
%\rb{usually though not always; as noted below there are other
%  approaches}\bcp{Yes, we have to be very careful about this}.
%\leo{Examples at a high level}: such as -- does not overwrite return addresses, or ...
Indeed, we are only aware of one---quite recent---attempt to frame a
positive definition:
\citet{Skorstengaard+19} define stack safety as
the conjunction of two properties, {\em local state encapsulation} and {\em
  well-bracketed control flow}.
They formalize these properties by defining an abstract capability-based machine
that ``satisfies [stack safety] by construction.''
%
Although this represents an important step in the right direction, we believe
there is still room to craft a more abstract, more generic characterization
of stack safety that is independent of capabilities or any other specific
enforcement
technique.  In other words, we seek formal criteria that can be applied
against \emph{any} stack-based system + enforcement mechanism to judge
whether or not the combination is actually stack-safe.

@@

The intuition behind \citet{Skorstengaard+19}'s\iflater\bcp{I forget how to
  remove the year and just have the author names here...}\fi use of the term {\em
  local state encapsulation} is that callers should be protected from
callees: a callee should be not be able to access or overwrite private data
in the caller's stack frame. We formalize this intuition as a security
property with both confidentiality and integrity components.
%
We reflect this intuition in a formal
{\em stack confidentiality} property, which promises that a callee's
observable behavior is not affected by memory outside its stack frame
(e.g. a caller's private data or uninitialized memory).  Conversely, {\em stack
  integrity} promises that, if a function call ever returns, the caller's
stack data at the point of return will be identical to what it was before
the call.

@@

We begin with a running example that will serve both to concretely
demonstrate the ``stack-unsafe'' behaviours we intend to preclude and to
ground and illustrate the formal properties and enforcement mechanisms in
later sections.

@@

First of all, we ignore the heap. We are mainly concerned with stack
interactions so that will be the main focus; integrating a safety
propety for the heap in the 
style of \citet{AzevedoDeAmorim17} is a natural extension we discuss
in~\Cref{sec:future}.
%
We also abstract away low-level details of memory layout and present a
machine that is word-addressed, with instructions starting from
location 0, a dedicated memory-mapped output port at location 99, and
the stack beginning at location 100 and growing upwards with increasing
addresses.  \leo{Explain more? How to connect to realistic
  one? Observations? DMA? Interrupt handlers?}
%
A sketch of the initial memory layout can be found in the top of
\cref{fig:running-trace-b}: instructions for {\tt main} begin at 0,
the dedicated output is uninitialized, while the (also uninitialized)
stack begins at 100. Directly below the layout, we summarize the parts
of the register file that are relevant to the example.
%
The rest of \cref{fig:running-trace-b} traces the execution of the
program, showing the machine state at call and return points.
Instructions are intended to
be similar to RISC-V, but are described in an ad-hoc notation
rather than using assembler syntax. The $\jal$ (jump-and-link)
instruction used for calls atomically saves the return address in a register
and jumps to a specified new $\PCname$; the $\jalr$ (jump-and-link-via-register)
instruction used for returns jumps to the address stored in a register.
Register $r_0$ is hardwired to zero. \leo{Expand upon this?}

@@

Stack safety is meant to protect a caller from a malicious callee's
attempts to access private data or highjack its control flow. Our
attacker model reflects this intention: we assume that the attacker
can run arbitrary code as a caller and the enforcement mechanism
should protect against that. Hardware and timing attacks are out of
scope. \leo{Anything else to add here?}
\leo{Maybe a good place to discuss calling conventions and that they
  are essentially enforced by the policy or sth?}
\rb{Intuition that the callee can do anything in principle, but the machine will
halt if it does not follow the calling convention, etc.?}

@@

The execution trace shown in \cref{fig:running-trace-b} is an example
of a ``stack-safe'' execution: each process interacts only with the
registers, its local stack space and its call frame. In the rest of
this section we'll go over examples of unsafe behaviors, before
formally capturing what stack-safe means formally and discussing
enforcement techniques from the literature in later sections. Throughout
the paper examples will be localize modifications of the example, by
substituting an instruction at a given PC, written:
\[\PCname :\mathit{inst}\]

@@

The choice of observations is an interesting one. A first approach
would be to consider any change to the registers or memory observable.
However, as some parts of the stack will be considered ``private''
this choice won't work. A relaxation of this to consider all changes
to ``non-private'' data observable could work in principle, but
doesn't allow for an interesting weaker-but-more-efficient enforcement
mechanism. We'll come back to this point in \Cref{sec:lazy}. On the
other hand, we could use a particular location as an abstract output
of our system (e.g. through DMA). This is the approach we chose for
our running example to keep things simple. For that, $\WORDS$ is the
set of 64-bit integers, $\REGS$ is the set $\{r_0, \cdots, r_{31}\}
\cup \{\PCname\}$, and $\SP = r_2$. Observations are the writes to the
special $\rout$ location: if during an execution step a word $w$ is
written to $\rout$ then $\obs = w$, otherwise $\obs = \tau$.

@@

\paragraph*{Null policy}
%
The simplest possible policy is the neutral policy that carries no information
and does nothing. Its set of policy states $\POLS$ is the unit type, and its
policy step function is the constant function that produces the unit, $\lambda
\_ . \top$, thereby allowing all calls the machine step function. Its
initialization function is defined on all states. This corresponds to the
lifting of our machine model to the policy setting. Machines that fulfill a
property by construction will also fulfill that property with the null
policy..

@@

A trace over a type $\TRACEELEMS$ is a nonempty, finite or infinite sequence of
$\TRACEELEMS$s. We will mostly be concerned with sequences of pairs of machine states
and observations, called machine traces and denoted $\machT \in \MOTRACE$,
and with sequences of triples of a machine state, a policy state, and an
observation, denoted $\MPT \in \MPOTRACE$ and referred to as MP-traces. 
observation, denoted $\MPT \in \MPOTRACE$ and referred to as MP-traces.

@@

In a similar fashion, we define \(\mpstatename \hookrightarrow_P \MPT\)
to relate a machine-policy state pair to the MP-trace
induced by \(\stepstopol{}\). Unlike the $\MOTRACE$ above, this trace can
be finite as the policy can cause a fault, in which case the final state is
a \(\tau\):

@@

\paragraph*{Until}
The ``Until'' operation \(\PUT(\Trace,f)\)
%\bcp{Wouldn't
%``While'' be more mnemonic?} \sna{Appealing, but it's more of a
%``while-not''? Trying out ``until''. In any case... moving away
%from doing joins means this needs to get some work to eliminate
%the trailing observation. Here's an attempt.}
takes a trace
\(\Trace : \mathit{trace} \TRACEELEMS \times \OBSS\) and a predicate
on elements \(f \subset \TRACEELEMS\) and gives the prefix of
\(\Trace\) ending with the first element on which \(f\) holds.
Subtly, because the observation associated with a trace represents its
next step, when we take a prefix from a trace containing observations
we must replace the final observation with a \(\tau\).

@@

In this section we will describe stack safety as a formal property. We
begin with our model of \leo{compiler-provided?} knowledge about the
program structure, and then dive in to formal definitions local state
encapsulation and well-bracketed control flow that together constitute
stack safety.

@@

As is standard with security properties, we associate with each
component of the machine a {\em label}: a pair of security levels
denoting high or low confidentiality and high or low integrity.
%
\[\mathit{label} ::= \{\HIGHSEC,\LOWSEC\} \times \{\HIGHINT,\LOWINT\}\]
%
In a traditional setting, integrity would enforce that the contents of
$\HIGHINT$ locations remain unchanged, while confidentiality would
enforce that the contents of $\HIGHSEC$ locations don't influence the
observable behavior of the machine. However, when dealing with nested
calls and returns, stack safety needs to enforce integrity and
confidentiality for {\em every} function call in a trace; that is, we
must treat the security level of data dynamically.
%
To that end, we introduce the notion of a {\em contour}, a map from
components to labels:
%
\[\contour \in \CONTOURS ::= \COMPONENTS \rightarrow \mathit{label}\]

@@

\definition{Transition} Given a trace $\MPT$, a call map $\callmap$ and
a code map $\codemap$, an $n$-{\em transition} a pair of
machine-policy state pairs $(\mach_c, \pol_c)$ and $(\mach_e, \pol_e)$
in the trace such that:
\begin{itemize}
\item one state pair steps to the other:
  $$\exists \obs. ~ (\mach_c, \pol_c) \stepstopol{\obs} (\mach_e, \pol_e),$$
\item $\mach_c$ is a valid call with $n$ arguments:
  $$\callmap(\mach_c(\PCname)) = n,$$
\item and $\mach_e$ is an entry point for $f$:
  $$\codemap(\mach_e(\PCname)) = f.$$
\end{itemize}

@@

For example, consider the unsafe substitution:
\[
42 : ~ \sw ~ r_4 ~ \rsp 100
\]
Instead of reading the proper argument, {\tt h} reads directly from the
secret value of {\tt x} that belongs to {\tt main}. \Cref{fig:confex}
shows \(\mach_e\), the entry state of {\tt h}, with high confidentiality memory
in \high and low confidentiality in \low. Below it, the variant state
\(\mach_e'\) agrees on low confidentiality memory, but all other addresses
hold -5, in orange. After the last step, the return states \(\mach_r\) and
\(\mach_r'\) should agree on every component that changed since \(\mach_e\) or
\(\mach_e'\). Addresses 108 and 109 have changed, shown in \tainted, and while 109
is consistent, 108 holds either 43 or -4, so the trace does not obey
trace confidentiality.
\rb{Color name macros}

@@

\definition{Stack Confidentiality}
Let $\callmap$ be a call map and $\codemap$ a code map. We say that a
system satisfies {\em stack confidentiality} with respect to
$\callmap$ and $\codemap$ if, for every initial machine-policy state
pair $(\mach_0, \pol_0)$ and its induced trace $\MPT$, and every
$n$-transition $(\mach_c, \pol_c)$ and $(\mach_e, \pol_e)$ to a callee
$f$ in $\MPT$, the following holds. Let $\MPT_{call}$ be the prefix where
\(\mpstate{\mach_e}{\pol_e} \hookrightarrow_P \MPT_{call} | \ret{\mach_c}\).
For each variant state \(\mach_e' \approx_{\mathit{Cof}(\mach_c, f, n)}
\mach_e\), let \(\machT\) be the similarly prefixed trace such that
\(\mach_e' \hookrightarrow \machT\). Then trace confidentiality holds on
\(\MPT_{call}\) and \(\machT\) with regard to \(\mathit{Cof}(\mach_c, f, n)\)
and \(R = \ret{\mach_c}\):

$$\forall \MPT_{call} ~ \machT. ~
\mpstate{\mach_e}{\pol_e} \hookrightarrow_P \MPT_{call} ~ | ~ \ret{\mach_c} \Rightarrow$$
$$\forall \mach_e'. ~ \mach_e \approx_{\mathit{Cof}(\mach_c, f, n)} \mach_e' \wedge
\mach_e' \hookrightarrow \machT ~ | ~ \ret{\mach_c} \Rightarrow$$
$$\mathit{conf}~\mathit{Cof}(\mach_c, f, n) ~ (\ret{\mach_c}) ~ \MPT_{call} ~ \machT_{call}$$

@@

Both the integrity and confidentiality components of local state
encapsulation concern themselves with the accessibility of data, and
may hold on a wide range of programs that violate expected control
flow. For example, if {\tt g} managed to jump in the middle of the
code of {\tt h} with its call, confidentiality and integrity would
still be satisfied.
%
However, that is still unwanted behavior: for example, a caller (or a
callee) should not be able to bypass a password check by jumping (or
returning) in the middle of a block of code - even if such an execution
would ostensibly satisfy local state encapsulation.
%
Stack safety is traditionally associated with preventing such unwanted
flows: every jump between functions should either be a call or a
return, and each return should to the instruction after its
corresponding call.

To formally capture this aspect of stack safety, we introduce three
security properties that rely on the underlying knowledge of the
program structure (code maps, function maps, return maps, and entry
maps): {\em control separation} ensures the validity of transition
sources between functions, {\em entry integrity} ensures the validity
of call targets, and {\tt return integrity} ensures the validity of
return targets.

@@

\definition{Well Bracketed Control Flow}

The above properties are somewhat orthogonal, but together they
capture a standard notion of control flow for a stack: functions keep
their code separate outside of calls and returns, calls respect
explicit entry points, and returns respect implicit entry points
corresponding to their call.  A system that enjoys them with regard to
a code, a call, a return, and an entry map is said to enjoy {\em well
  bracketed control flow} with regard to those maps.

@@

\definition{Variant stacks}
  The testing property keeps track of execution information on a stack whose
  elements record an initial machine, an initial and current variant of the
  machine, a contour and a return map:
  $$\vse \in \VSES ::= \MACHS \times \MACHS \times \MACHS \times \CONTOURS \times 2^\MACHS)$$
  $$\vse = (\mathit{init\_machine}(\vse), \mathit{init\_variant}(\vse), \mathit{curr\_variant}(\vse), \contour(\vse), \mathit{ret}(\vse))$$
  $$\vs \in \VSS$$
  Given the current machine state $\mach$, a stack $\vs$ is \emph{well-formed}
  with respect to it if:
  \begin{itemize}
  \item The current variant is indeed a variant of the current state.
  \item The stack is nonempty and the bottom return map is the false property.
  \item The current state is in the trace of every initial machine.
  \item The variant state is in the trace of its own initial variant.
  \item The return function is in the return map if not the last element. \rb{TODO}
  \item All contours have public registers.
  \end{itemize}

>>>>

But what {\em is} this ``stack safety'' of which we speak? Precise formal
definitions are lacking in the literature; instead, the notion
is usually defined negatively, by enumerating the bad things that a given
enforcement mechanism
prevents, such as corruption of return addresses, buffer overflows, or
use of uninitialized variables.
%with the notion usually being
%defined negatively: through examples of stack-based exploits
%\rb{usually though not always; as noted below there are other
%  approaches}\bcp{Yes, we have to be very careful about this}.
%\leo{Examples at a high level}: such as -- does not overwrite return addresses, or ...
Indeed, we are only aware of one---quite recent---attempt to frame a
positive definition:
\citet{Skorstengaard+19} define stack safety as
the conjunction of two properties, {\em local state encapsulation} and {\em
  well-bracketed control flow}.
They formalize these properties by defining an abstract capability-based machine
that ``satisfies [stack safety] by construction.''
%
Although this represents an important step in the right direction, we believe
there is still room to craft a more abstract, more generic characterization
of stack safety that is independent of capabilities or any other specific
enforcement
technique.  In other words, we seek formal criteria that can be applied
against \emph{any} stack-based system + \rb{in words or symbols? :-)} enforcement mechanism to judge
whether or not the combination is actually stack-safe.

@@

The intuition behind \citet{Skorstengaard+19}'s \iflater\bcp{I forget how to
  remove the year and just have the author names here...}\fi use of the term {\em
  local state encapsulation} is that callers should be protected from
callees: a callee should be not be able to access or overwrite private data
in the caller's stack frame. We formalize this intuition as a security
property with both confidentiality and integrity components.
%
We reflect this intuition in a formal
{\em stack confidentiality} property, which promises that a callee's
observable behavior is not affected by memory outside its stack frame
(e.g., a caller's private data or uninitialized memory).  Conversely, {\em stack
  integrity} promises that, if a function call ever returns, the caller's
stack data at the point of return will be identical to what it was before
the call.

@@

We begin with a running example that will serve both to concretely
demonstrate the ``stack-unsafe'' behaviors we intend to preclude and to
ground and illustrate the formal properties and enforcement mechanisms in
later sections.

@@

First of all, we ignore the heap. We are mainly concerned with stack
interactions so that will be the main focus; integrating a safety
propety for the heap in the 
style of \citet{AzevedoDeAmorim17} is a natural extension we discuss
in~\Cref{sec:future}.
%
We also abstract away low-level details of memory layout and present a
machine that is word-addressed, with instructions starting from
location 0, a dedicated memory-mapped output port at location 99, and
the stack beginning at location 100 and growing upwards with increasing
addresses.  \leo{Explain more? How to connect to realistic
  one? Observations? DMA? Interrupt handlers?}
%
A sketch of the initial memory layout can be found at the top of
\cref{fig:running-trace-b}: instructions for {\tt main} begin at 0,
the dedicated output is uninitialized, while the (also uninitialized)
stack begins at 100. Directly below the layout, we summarize the parts
of the register file that are relevant to the example.
%
The rest of \cref{fig:running-trace-b} traces the execution of the
program, showing the machine state at call and return points.
Instructions are intended to
be similar to RISC-V, but are described in an ad-hoc notation
rather than using assembler syntax. The $\jal$ (jump-and-link)
instruction used for calls atomically saves the return address in a register
and jumps to a specified new $\PCname$; the $\jalr$ (jump-and-link-via-register)
instruction used for returns jumps to the address stored in a register.
Register $r_0$ is hardwired to zero. \leo{Expand upon this?}

@@

Stack safety is meant to protect a caller from a malicious callee's
attempts to access private data or hijack its control flow. Our
attacker model reflects this intention: we assume that the attacker
can run arbitrary code as a caller and the enforcement mechanism
should protect against that. Hardware and timing attacks are out of
scope. \leo{Anything else to add here?}
\leo{Maybe a good place to discuss calling conventions and that they
  are essentially enforced by the policy or sth?}
\rb{Intuition that the callee can do anything in principle, but the machine will
halt if it does not follow the calling convention, etc.?}

@@

The execution trace shown in \cref{fig:running-trace-b} is an example
of a ``stack-safe'' execution: each process interacts only with the
registers, its local stack space and its call frame. In the rest of
this section we will go over examples of unsafe behaviors, before
formally capturing what stack-safe means formally and discussing
enforcement techniques from the literature in later sections. Throughout
the paper examples will be localized modifications of the example, by
substituting an instruction at a given PC, written:
\[\PCname :\mathit{inst}\]

@@

The choice of observations is an interesting one. A first approach
would be to consider any change to the registers or memory as observable.
However, as some parts of the stack will be considered ``private''
this choice won't work. A relaxation of this to consider all changes
to ``non-private'' data as observable could work in principle, but
does not allow for an interesting weaker-but-more-efficient enforcement
mechanism. We will come back to this point in \Cref{sec:lazy}. On the
other hand, we could use a particular location as an abstract output
of our system (e.g., through DMA). This is the approach we chose for
our running example to keep things simple. For that, $\WORDS$ is the
set of 64-bit integers, $\REGS$ is the set $\{r_0, \cdots, r_{31}\}
\cup \{\PCname\}$, and $\SP = r_2$. Observations are the writes to the
special $\rout$ location: if during an execution step a word $w$ is
written to $\rout$ then $\obs = w$, otherwise $\obs = \tau$.

@@

\paragraph*{Null policy}
%
The simplest possible policy is the neutral policy that carries no information
and does nothing. Its set of policy states $\POLS$ is the unit type, and its
policy step function is the constant function that produces the unit, $\lambda
\_ . \top$, thereby allowing all calls the machine step function. Its
initialization function is defined on all states. This corresponds to the
lifting of our machine model to the policy setting. Machines that fulfill a
property by construction will also fulfill that property with the null
policy.

@@

A trace over a type $\TRACEELEMS$ is a nonempty, finite or infinite sequence of
$\TRACEELEMS$s. We will mostly be concerned with sequences of pairs of machine states
and observations, called machine traces and denoted $\machT \in \MOTRACE$,
and with sequences of triples of a machine state, a policy state, and an
observation, denoted $\MPT \in \MPOTRACE$ and referred to as MP-traces.

@@

In a similar fashion, we define \(\mpstatename \hookrightarrow_P \MPT\)
to relate a machine-policy state pair to the MP-trace
induced by \(\stepstopol{}\). Unlike the $\MOTRACE$ above, this trace can
be finite as the policy can cause a fault, in which case the final state is
a \(\tau\):
\rb{This $\hookrightarrow_P$ is often enough written just $\hookrightarrow$.
Overload everywhere?}

@@

\paragraph*{Until}
The ``Until'' operation \(\PUT(\Trace,f)\)
%\bcp{Wouldn't
%``While'' be more mnemonic?} \sna{Appealing, but it's more of a
%``while-not''? Trying out ``until''. In any case... moving away
%from doing joins means this needs to get some work to eliminate
%the trailing observation. Here's an attempt.}
takes a trace
\(\Trace : \mathit{trace} ~ \TRACEELEMS \times \OBSS\) and a predicate
on elements \(f \subset \TRACEELEMS\) and gives the prefix of
\(\Trace\) ending with the first element on which \(f\) holds.
Subtly, because the observation associated with a trace represents its
next step, when we take a prefix from a trace containing observations
we must replace the final observation with a \(\tau\).

@@

In this section we will describe stack safety as a formal property. We
begin with our model of \leo{compiler-provided?} knowledge about the
program structure, and then dive into the formal definitions of local state
encapsulation and well-bracketed control flow that together constitute
stack safety.

@@

As is standard with security properties, we associate with each
component of the machine a {\em label}: a pair of security levels
denoting high or low confidentiality and high or low integrity.
%
\[\mathit{label} ::= \{\HIGHSEC,\LOWSEC\} \times \{\HIGHINT,\LOWINT\}\]
%
In a traditional setting, integrity would enforce that the contents of
$\HIGHINT$ locations remain unchanged, while confidentiality would
enforce that the contents of $\HIGHSEC$ locations do not influence the
observable behavior of the machine. However, when dealing with nested
calls and returns, stack safety needs to enforce integrity and
confidentiality for {\em every} function call in a trace; that is, we
must treat the security level of data dynamically.
%
To that end, we introduce the notion of a {\em contour}, a map from
components to labels:
%
\[\contour \in \CONTOURS ::= \COMPONENTS \rightarrow \mathit{label}\]

@@

\definition{Transition} Given a trace $\MPT$, a call map $\callmap$ and
a code map $\codemap$, an $n$-{\em transition} is a pair of
machine-policy state pairs $(\mach_c, \pol_c)$ and $(\mach_e, \pol_e)$
in the trace such that:
\begin{itemize}
\item one state pair steps to the other:
  $$\exists \obs. ~ (\mach_c, \pol_c) \stepstopol{\obs} (\mach_e, \pol_e),$$
\item $\mach_c$ is a valid call with $n$ arguments:
  $$\callmap(\mach_c(\PCname)) = n,$$
\item and $\mach_e$ is an entry point for $f$:
  $$\codemap(\mach_e(\PCname)) = f.$$
\end{itemize}

@@

For example, consider the unsafe substitution:
\[
42 : ~ \sw ~ r_4 ~ \rsp 100
\]
Instead of reading the proper argument, {\tt h} reads directly from the
secret value of {\tt x} that belongs to {\tt main}. \Cref{fig:confex}
shows \(\mach_e\), the entry state of {\tt h}, with high confidentiality memory
in {\high} and low confidentiality in \low. Below it, the variant state
\(\mach_e'\) agrees on low confidentiality memory, but all other addresses
hold -5, in orange. After the last step, the return states \(\mach_r\) and
\(\mach_r'\) should agree on every component that changed since \(\mach_e\) or
\(\mach_e'\). Addresses 108 and 109 have changed, shown in \tainted, and while 109
is consistent, 108 holds either 43 or -4, so the trace does not obey
trace confidentiality.
\rb{Color name macros}

@@

\definition{Stack Confidentiality}
Let $\callmap$ be a call map and $\codemap$ a code map. We say that a
system satisfies {\em stack confidentiality} with respect to
$\callmap$ and $\codemap$ if, for every initial machine-policy state
pair $(\mach_0, \pol_0)$ and its induced trace $\MPT$, and every
$n$-transition $(\mach_c, \pol_c)$ and $(\mach_e, \pol_e)$ to a callee
$f$ in $\MPT$, the following holds. Let $\MPT_{\mathit{call}}$ be the prefix where
\(\mpstate{\mach_e}{\pol_e} \hookrightarrow_P \MPT_{\mathit{call}} | \ret{\mach_c}\).
For each variant state \(\mach_e' \approx_{\mathit{Cof}(\mach_c, f, n)}
\mach_e\), let \(\machT\) be the similarly prefixed trace such that
\(\mach_e' \hookrightarrow \machT\). Then trace confidentiality holds on
\(\MPT_{\mathit{call}}\) and \(\machT\) with regard to \(\mathit{Cof}(\mach_c, f, n)\)
and \(R = \ret{\mach_c}\):

$$\forall \MPT_{\mathit{call}} ~ \machT. ~
\mpstate{\mach_e}{\pol_e} \hookrightarrow_P \MPT_{\mathit{call}} ~ | ~ \ret{\mach_c} \Rightarrow$$
$$\forall \mach_e'. ~ \mach_e \approx_{\mathit{Cof}(\mach_c, f, n)} \mach_e' \wedge
\mach_e' \hookrightarrow \machT ~ | ~ \ret{\mach_c} \Rightarrow$$
$$\mathit{conf}~\mathit{Cof}(\mach_c, f, n) ~ (\ret{\mach_c}) ~ \MPT_{\mathit{call}} ~ \machT_{\mathit{call}}$$

@@

Both the integrity and confidentiality components of local state
encapsulation concern themselves with the accessibility of data, and
may hold on a wide range of programs that violate expected control
flow. Say, if {\tt g} managed to jump in the middle of the
code of {\tt h} with its call, confidentiality and integrity would
still be satisfied.
%
However, that is still unwanted behavior: for example, a caller (or a
callee) should not be able to bypass a password check by jumping (or
returning) in the middle of a block of code --- even if such an execution
would ostensibly satisfy local state encapsulation.
%
Stack safety is traditionally associated with preventing such unwanted
flows: every jump between functions should either be a call or a
return, and each return should be to the instruction after its
corresponding call.

To formally capture this aspect of stack safety, we introduce three
security properties that rely on the underlying knowledge of the
program structure (code maps, function maps, return maps, and entry
maps): {\em control separation} ensures the validity of transition
sources between functions, {\em entry integrity} ensures the validity
of call targets, and {\em return integrity} ensures the validity of
return targets.

@@

\definition{Well-Bracketed Control Flow}

The above properties are somewhat orthogonal, but together they
capture a standard notion of control flow for a stack: functions keep
their code separate outside of calls and returns, calls respect
explicit entry points, and returns respect implicit entry points
corresponding to their call.  A system that enjoys them with regard to
a code, a call, a return, and an entry map is said to enjoy
{\em well-bracketed control flow} with regard to those maps.

@@

\definition{Variant stacks}
  The testing property keeps track of execution information on a stack whose
  elements record an initial machine, an initial and current variant of the
  machine, a contour and a return map:
  $$\vse \in \VSES ::= \MACHS \times \MACHS \times \MACHS \times \CONTOURS \times \RETMAPS$$
  $$\vse = (\mathit{init\_machine}(\vse), \mathit{init\_variant}(\vse), \mathit{curr\_variant}(\vse), \contour(\vse), \mathit{ret}(\vse))$$
  $$\vs \in \VSS$$
  Given the current machine state $\mach$, a stack $\vs$ is \emph{well-formed}
  with respect to it if:
  \begin{itemize}
  \item The current variant is indeed a variant of the current state.
  \item The stack is nonempty and the bottom return map is the false property.
  \item The current state is in the trace of every initial machine.
  \item The variant state is in the trace of its own initial variant.
  \item The return function is in the return map if not the last element. \rb{TODO}
  \item All contours have public registers.
  \end{itemize}
